---
title: "Data Analysis"
author: "Gabriel"
date: "March 18, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
#defining the working directory
getwd()
setwd("C:/Users/GHOOST/Desktop/New Lit/data")
```

```{r include=FALSE}
#attaching the packages
library(car)
library(foreign)
library(ggplot2)
library(summarytools)
library(knitr)
```


```{r include=FALSE}
#attaching the data

data<-read.csv("International Students Survey.csv")

attach(data)
```


```{r include=FALSE}
#Data preparation
#Age
table(Age)

summary(as.numeric(Age))

data$age<-recode(as.numeric(Age),"17:21=1; 22:26=2;27:hi=3")

table(data$age)

data$age<-factor(data$age,lab=c("17 to 21 yrs", "22 to 26 yrs", " 27 yrs and older")) 

```


```{r include=FALSE}
#country regions
data$region[data$Home.country == 'Algeria'| 
    data$Home.country == 'Botswana'| data$Home.country == 'Cameroon'|
    data$Home.country == 'Chad'| data$Home.country == 'Congo'|
    data$Home.country == 'DR Congo'|data$Home.country == 'Eritrea'|
    data$Home.country == 'Ivory Coast'|
    data$Home.country == 'Gambia'|data$Home.country == 'Ghana'|
    data$Home.country == 'Kenya'|data$Home.country == 'Madagascar'|
    data$Home.country == 'Niger'|data$Home.country == 'Nigeria'|
    data$Home.country == 'South Africa'|data$Home.country == 'Sudan'|
    data$Home.country == 'Uganda'|data$Home.country == 'Zambia'] <- 'Africa'


data$region[data$Home.country == 'Australia'| data$Home.country == 'Austria'| 
    data$Home.country == 'Bosnia and Herzegovina'|
    data$Home.country == 'Bulgaria'| data$Home.country == 'Europe'|
    data$Home.country == 'France'| data$Home.country == 'Germany'|
    data$Home.country == 'Italy'|data$Home.country == 'Poland'|
    data$Home.country == 'Portugal'|data$Home.country == 'Serbia'|
    data$Home.country == 'Spain'|data$Home.country == 'Switzerland'|
    data$Home.country == 'Republic of North Macedonia'|
    data$Home.country == 'USA'] <- 'Europe, USA & Australia'


data$region[data$Home.country == 'Armenia'| 
    data$Home.country == 'Azerbaijan'|data$Home.country == 'Belarus'|
    data$Home.country == 'Estonia'|data$Home.country == 'Georgia'|
    data$Home.country == 'Georgia'|data$Home.country == 'Kazakhstan'|
    data$Home.country == 'Kyrgyzstan'|data$Home.country == 'Latvia'|
    data$Home.country == 'Moldova'|data$Home.country == 'Tajikistan'|
    data$Home.country == 'Turkmenistan'|data$Home.country == 'Ukraine'|
    data$Home.country == 'Uzbekistan'] <- 'Former Soviet Republics'


data$region[data$Home.country == 'Bahrain'| 
    data$Home.country == 'Egypt'| data$Home.country == 'Iran'|
    data$Home.country == 'Israel'| data$Home.country == 'Lebanon'|
    data$Home.country == 'Syria'| 
    data$Home.country == 'Turkey'] <- 'Middle East'


data$region[data$Home.country == 'Bangladesh'| 
    data$Home.country == 'India'| data$Home.country == 'Nepal'|
    data$Home.country == 'Pakistan'| 
    data$Home.country == 'Sri Lanka'] <- 'Southern Asia'

data$region[data$Home.country == 'Brazil'| 
    data$Home.country == 'Colombia'|data$Home.country == 'Ecuador'|
    data$Home.country == 'Guatemala'| data$Home.country == 'Haiti'|
    data$Home.country == 'Mexico'|
    data$Home.country == 'Nicaragua'] <- 'Southern America'

data$region[data$Home.country == 'China'| 
    data$Home.country == 'Japan'|data$Home.country == 'Mongolia'| 
    data$Home.country == 'South Korea'|data$Home.country == 'Hong Kong'|
    data$Home.country == 'Taiwan'] <- 'Eastern Asia'

data$region[data$Home.country == 'Indonesia'|
    data$Home.country == 'Philippines'|data$Home.country == 'Thailand'|
    data$Home.country == 'Vietnam'] <- 'Southern Eastern Asia'

table(data$region, useNA = "ifany")

attach(data)

```


##Data Analysis

This section presents a description of the demographic information of the respondents. 

#Demographic information

```{r}
#degree

freq(What.degree.are.you.currently.studying.for.)

ggplot(data, aes(x=What.degree.are.you.currently.studying.for., fill=region)) + geom_bar() + labs(title="Degree")

```
The table presents the shares of respondents pursuing their degrees. It shows that 58% of the respondents are pursuing their masters studies, 41% whilst 1% are in their preparatory year. 
The plot presents the level of education of respondents with reference to their region of origin. It can be seen that majority of students are from Former Soviet Republics.  


```{r}
#language of instruction
freq(What.is.the.language.of.instruction.for.your.program.)

plot2 <- ggplot(data, aes(x=What.is.the.language.of.instruction.for.your.program., fill=region)) + geom_bar() + labs(title="Language of instruction")
print(plot2)

```
The table presents the shares of the language of instruction for the programs respondents are studying. Majority of the respondents 61% are taking programs in Russian whilst 39% are studying in English programs. The plot shows that students from Africa dominate students taking the English programs whilst students from the former Soviet Republics are in the majority for respondents taking Russian programs.  


```{r}
#Gender
freq(Gender)

ggplot(data, aes(x=Gender, fill=region)) + geom_bar() + labs(title="Gender")

```
The table reports that 52% of the respondents are females whilst 47% are males. the plots presents the gender distribution across the regions.



```{r}
#Age
freq(age)

ggplot(data, aes(x=age, fill=region)) + geom_bar() + labs(title="Age")

```
The table reports that 48% of the respondents are within the age range (22 to 26 yrs), 35% are within the age range (17 to 21 yrs) and 18% are within the age cohort of 27 yrs and older. The plot presents the age distribution across the regions.


##Factors influencing the decision to study in Russia
This section presents the factors that influenced the decision of international students to study in Russia. It will establish the push factors that account for students decision to leave their home country and the pull factors in Russia and HSE that influenced their decision to study. Finally, this section will present a linear regression to explain statistically significant push and pull factors.    

The influence of the push factors was measured with a scale of 1 (not at all influential), 2 (slightly ifluential), 3 (somewhat influential), 4 (very influential) and 5 (extremely influential).For the purposes of this analysis, the shares of scales 1 and 2 will be summed up and presented as 'not at all influential'. Similar aggregation will be done for scales 4 and 5 with the resulting scale presented as very influential. the scale 3 will be to depict respondents' uncertainty on a factors influence.

#push factors in Home country (Descriptive analysis)
The factors that influnced respondents' decision to leave their home country and study abroad is discussed in the ensuing paragraphs. .


```{r}
#unavailable program
freq(Unavailability.of.the.desired.study.program)

ggplot(data, aes(x=Unavailability.of.the.desired.study.program, fill=region)) + geom_bar() + labs(title="Unavailable program")

```
The results show that majority of respondents with shares (47%) reported that the unavailability of the desired program accounted for their decision to leave their home country and study abroad. The plot presents the distribution of this push factor across the regions with its position prominent among students from the Former Soviet Republics and Africa. 


```{r}
#low quality of education
freq(Low.quality.of.education)

ggplot(data, aes(x=Low.quality.of.education, fill=region)) + geom_bar() + labs(title="Low quality of education")

```
The results reflect that low quality of education (with shares 50%) also account for respondents decison to leave their home country.  The plot shows that the influence of this push factor is dominant among students from the Former Soviet Republics, Africa, Eastern Asia and Southern Eastern Asia. 


```{r}
#competitive University admission in home country
freq(Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution)

ggplot(data, aes(x=Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution, fill=region)) + geom_bar() + labs(title="Competitive University Admission")

```
Majority of the respondents (47%) reported that difficulty in gaining admission to a quality local institution was not influential in their decision to leave their home country. This position, as depicted in the graph, is held by students from the Former Soviet Republics,Africa and Europe, USA & Australia.


```{r}
#Advantage of international degree
freq(Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market)

ggplot(data, aes(x=Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market, fill=region)) + geom_bar() + labs(title="Perceived advantage of internatioal degree")

```
The result highlights the position that the perceived advantage of international degree over a local one in the home country (with shares 59%) was influential in respondents decision to study abroad. 


```{r}
#Unavailability of scholarship
freq(Unavailability.of.scholarship.opportunities)

ggplot(data, aes(x=Unavailability.of.scholarship.opportunities, fill=region)) + geom_bar() + labs(title="Unavailability of scholarship")

```
The result show that majority of the respondents (44%) reflect that the unavailability of scholarship opportunities was not influential in their decision to leave their home country. 


```{r}
#encouragement from family
freq(Encouragement.from.my.family.to.study.abroad)

ggplot(data, aes(x=Encouragement.from.my.family.to.study.abroad, fill=region)) + geom_bar() + labs(title="Encouragement from family")

```
The result show that majority of the respondents (46%) report that their decision to study abroad was influenced by encouragement of their family.


```{r}
#encouragement from friends
freq(Encouragement.from..my.friends.to.study.abroad)

ggplot(data, aes(x=Encouragement.from..my.friends.to.study.abroad, fill=region)) + geom_bar() + labs(title="Encouragement from friends")

```
The result show that the respondents were uncertain of the influence of the encouragement of their friends in their decision to study abroad.


```{r}
#Better earning prospects abroad
freq(Better.earning.prospects.abroad)

ggplot(data, aes(x=Better.earning.prospects.abroad, fill=region)) + geom_bar() + labs(title="Better earning prospects")

```
With the factor, better earning prospects abroad majority of respondents (64%) reported that it was very influential in their decision to stduy abroad. 


```{r}
#social prestige
freq(The.social.prestige.of.studying.abroad)

ggplot(data, aes(x=The.social.prestige.of.studying.abroad , fill=region)) + geom_bar() + labs(title="The.social.prestige.of.studying.abroad")

```
Majority of the respondents (61%) revealed that the social prestige associated with studying abroad was very influential in their decision to study abroad.


```{r}
#Experience different culture
freq(To.experience.a.different.culture)

ggplot(data, aes(x=To.experience.a.different.culture, fill=region)) + geom_bar() + labs(title="EXperience different culture")

```
Majority of the respondents (56%) reported that the decision to study abroad was influenced by their desire to experience a different culture. 


#push factors in Home country (Regression analysis)

empty model
```{r include=FALSE}
model0<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~1, data = data)

summary(model0)

```


Full Model
```{r include=FALSE}

model1<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+Unavailability.of.scholarship.opportunities+Encouragement.from.my.family.to.study.abroad+Encouragement.from..my.friends.to.study.abroad+Better.earning.prospects.abroad+The.social.prestige.of.studying.abroad+To.experience.a.different.culture, data=data)

summary(model1)

```


Results
```{r}
kable(summary(model1)$coef, digits = 2, caption = "Push factors")
```

The table displays the results of the full regression model to highlight the association between the push factors and the decision to study abroad. The model has a R2 of 0.138 which means that approximately the model can explain 14% of the decision to study abroad as such translates to the goodness of the results. 
The following factors realized significance; competitive university admission process, perceived advantage of international degree, the social prestige of studying abroad and to experience a different culture. 


#pull factors (Descriptive analysis)
The factors in Russia and HSE that infleunced respondents' decision to pursue their studies in Russia


```{r}
#Availablility of desired program
freq(Availability.of.desired.study.program)

ggplot(data, aes(x=Availability.of.desired.study.program, fill=region)) + geom_bar() + labs(title="Availability of desired study program")

```
Majority of the respondents (68%) revealed that the availability of the desired study program  was very influential in their decision to study in Russia.


```{r}
#high quality of education
freq(Higher.quality.of.education..compared.to.home.country.)

ggplot(data, aes(x=Higher.quality.of.education..compared.to.home.country., fill=region)) + geom_bar() + labs(title="High quality of education")

```
Majority of the respondents (68%) considered the quality of education in Russia to be higher in comparison with their home country and as such very influential in their decision to study in Russia.


```{r}
#low cost of living
freq(Low.cost.of.living)

ggplot(data, aes(x=Low.cost.of.living, fill=region)) + geom_bar() + labs(title="Low cost of living")

```
The result show that the respondents were uncertain of the influence of low cost of living as a factor in their decision to study in Russia.


```{r}
#tuition fees
freq(Low.tuition.fees)

freq(Cost.of.tuition.for.international.students)

ggplot(data, aes(x=Low.tuition.fees, fill=region)) + geom_bar() + labs(title="Low tuition fees")

ggplot(data, aes(x=Cost.of.tuition.for.international.students, fill=region)) + geom_bar() + labs(title="Cost of tuition")

```
Respondents were asked about the influence of the cost of tuition on their decision to study in Russia. The results show that majority of the respondents' (44%) decision to study in Russia was influenced by the low cost of tuition. Similarly, majority of the respondents (66%) reported that their decision to study in HSE was influenced by the University's cost of tuition for international students.



```{r}
#Scholarships
freq(Awarded.scholarships.or.tuition.waiver)
freq(Availability.of.scholarships)


ggplot(data, aes(x=Awarded.scholarships.or.tuition.waiver, fill=region)) + geom_bar() + labs(title="Scholarship or tuition waiver")

ggplot(data, aes(x=Availability.of.scholarships, fill=region)) + geom_bar() + labs(title="Availability of scholarships")

```
On the influence of scholarship on students' decision to study in Russia,  respondents (57%) reported that awarded scholarship and tuition waivers were influential in their decision to study in Russia. The results also reported that respondents (68%) decsion to stduy in Russia were influenced by the availability of scholarships in HSE. 



```{r}
#Attraction to Russian culture
freq(Attraction.to.Russian.culture..society)

ggplot(data, aes(x=Attraction.to.Russian.culture..society, fill=region)) + geom_bar() + labs(title="Attraction to Russian culture")

```
The results show that majority of the respondents' (45%) decision to study in Russia was heavily influenced by their attraction to the Russian culture.



```{r}
#career prospects in Russia
freq(Career.prospects.in.Russia)

ggplot(data, aes(x=Career.prospects.in.Russia, fill=region)) + geom_bar() + labs(title="Career prospects in Russia")

```
The results show that majority of the respondents (45%) report that career prospects in Russia was very influential in their decision to study in Russia. 


```{r}
#recommendations from family and friends
freq(Personal.recommendations.from.parents..relatives..and.friends)

ggplot(data, aes(x=Personal.recommendations.from.parents..relatives..and.friends, fill=region)) + geom_bar() + labs(title="Recommendations from family and friends")

```
A significant number of respondents (40%) reported that their decision to study in Russia was influenced by recommendations from family and friends.

 

```{r}
#Cultural proximity
freq(cultural.proximity.with.home)

ggplot(data, aes(x=cultural.proximity.with.home, fill=region)) + geom_bar() + labs(title="Cultural proximity")

```
The results show that cultural proximity was not very influential in defining respondents (43%) decision to study in Russia.


```{r}
#geographical proximity
freq(geographical.proximity.with.home)

ggplot(data, aes(x=geographical.proximity.with.home, fill=region)) + geom_bar() + labs(title="Geograhical proximity")

```
Similarly, the results show that geographical proximity was not influential in respondents (47%) decision to study in Russia. 



```{r}
#quality and reputation
freq(Quality.and.reputation.of.the.University)

ggplot(data, aes(x=Quality.and.reputation.of.the.University, fill=region)) + geom_bar() + labs(title="Quality and reputation of HSE")

```
The results show that majority of the respondents (86%) reported that the quality and reputation of HSE was very influential in their decision to study in Russia.


```{r}
#recognition of degree
freq(Recognition.of.the.degree.in.my.home.country)

ggplot(data, aes(x=Recognition.of.the.degree.in.my.home.country, fill=region)) + geom_bar() + labs(title="Recognition of degree")

```
The results show that majority of the respondents (53%) reported that the recognition of HSE's degree in their home country was very influential in their decision to study in Russia.


```{r}
#quality of teachers
freq(Quality.of.the.teaching.staff)

ggplot(data, aes(x=Quality.of.the.teaching.staff, fill=region)) + geom_bar() + labs(title="Quality of teachers")

```
The results show that majority of the respondents (69%) reported that the quality of HSE's teachers was very influential in their decision to study in Russia.



```{r}
#reputation of alumni
freq(The.reputation.of.the.alumni)

ggplot(data, aes(x=The.reputation.of.the.alumni, fill=region)) + geom_bar() + labs(title="Reputation of alumni")

```
The results show that majority of the respondents (50%) reported that the reputation of HSE's alumni was very influential in their decision to study in Russia.



```{r}
#HSE rank
freq(HSE.position.in.international.university.rankings)

ggplot(data, aes(x=HSE.position.in.international.university.rankings, fill=region)) + geom_bar() + labs(title="HSE's rank")

```
The results show that majority of the respondents (66%) reported that HSE's position in international university rankings was very influential in their decision to study in Russia.


```{r}
#support for international students
freq(Support.services.for.international.students)

ggplot(data, aes(x=Support.services.for.international.students, fill=region)) + geom_bar() + labs(title="Support services for international students")

```
The results show that the respondents (50%) reported that HSE's support for international students was very influential in their decision to study in Russia.



```{r}
#HSE alliances
freq(HSE.s.international.strategic.alliances)

ggplot(data, aes(x=HSE.s.international.strategic.alliances, fill=region)) + geom_bar() + labs(title="HSE alliances")

```
The results show that the respondents (47%) reported that HSE's strategic alliances with other institutions was influential in their decision to study in Russia.


```{r}
#Local preference for HSE degrees
freq(Local.employers.preference.of..degrees.awarded.by.HSE)

ggplot(data, aes(x=Local.employers.preference.of..degrees.awarded.by.HSE, fill=region)) + geom_bar() + labs(title="Local preference for HSE degrees")

```
The results show that the respondents (50%) reported that local employers preference for HSE's degree was very influential in their decision to study in Russia.


```{r}
#Graduate employment rates
freq(Graduates.employment.rates)

ggplot(data, aes(x=Graduates.employment.rates, fill=region)) + geom_bar() + labs(title="Graduate employment rate")

```
The results show that the respondents (53%) reported that HSE's graduate employment rates was very influential in their decision to study in Russia.


#Pull factors (Regression analysis)

empty model
```{r include=FALSE}
model0<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~1, data = data)

summary(model0)

```


Full Model
```{r include=FALSE}

model2<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home+Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE, data=data)

summary(model2)
```


Results
```{r}
kable(summary(model2)$coef, digits = 2, caption = "Pull factors")
```

The table displays the results of the full regression model to highlight the association between the pull factors and the decision to study abroad. The model has a R2 of 0.214 which means that approximately the model can explain 21% of the decision to study in Russia and this highlights the goodness of the results. 
The following factors realized significance; availability of desired study program, higher quality of education compared to home country, low cost of living, attraction to Russian culture, and graduates employment rates.


##Post graduation migration plans
This section highlights students' post migration plans

#graduation plans

```{r}
freq(What.are.your.plans.after.graduation.)
ggplot(data, aes(x=What.are.your.plans.after.graduation., fill=region)) + geom_bar() + labs(title="Post graduation migration plans")

```
This results show the distribution of respondents and their post graduation migration plans. 37% of the respondents reported that they intended to move to another country after graduation, 38% reported they intended to stay in Russia and 23% wanted to return home. 

#Staying in Russia (Descriptive analysis)

Reason for staying in Russia

```{r}
#job opportunities
freq(Better.job.opportunities..in.comparison.with.home.country.)
```
This show that the respondents' decision to stay in Russia after graduation is influenced by better job opportunities in Russia as compared to the home country.


```{r}
#quality of life
freq(Higher.quality.of.life..in.comparison.with.home.country.)
```
This show that the respondents' decision to stay in Russia after graduation is influenced by higher quality of life in Russia as compared to the home country.


```{r}
#career opportunities
freq(Better.career.opportunities.and.advancement.in.chosen.profession)
```
This show that the respondents' decision to stay in Russia after graduation is influenced by better career opportunities in Russia.


```{r}
#income level
freq(Higher.income.level)
```
This show that the respondents' decision to stay in Russia after graduation is influenced by higher income level in Russia.


```{r}
#ties to family and friends
freq(Ties.to.family.and.friends)
```
This show that the respondents' decision to stay in Russia after graduation is influenced by ties to family and friends in Russia.


```{r}
#international experience
freq(Gain.international.experience)

```
This show that the respondents' decision to stay in Russia after graduation is influenced by their desire to gain international experience. 


Reasons for not returning home but stay in Russia
```{r}
#family expectations
freq(Family.expectations)
```
This shows that the respondents' are uncertain about the influence of family expectations in their decision to not return home after graduation. 


```{r}
#cultural practices
freq(Restrictive.cultural.practices..eg..pressure.to.marry.)
```
This shows that cultural practices was not influential in respondents' decision to not return home after graduation. 


```{r}
#limited job opportunitiesin Home country
freq(Limited.job.opportunities.in.home.country)

```
This shows that limited job opportunities in home country was influential in respondents' decision to not return home after graduation. 


```{r}
#income levels
freq(Lower.income.levels)
```
Respondents reported that lower income levels in their home country was influential in their decision to not return home after graduation.

```{r}
#quality of life
freq(Lower.quality.of.life.2)
```
Respondents reported that lower quality of life in their home country was influential in their decision to not return home after graduation.

```{r}

#political persecution
freq(Political.persecution)

```
This shows that fear of political persecution was not influential in respondents' decision to not return home after graduation. 


```{r}
#danger to one's life
freq(Danger.or.fear.for.one.s.own.life)
```
This shows that danger to one's own life was not influential in respondents' decision to not return home after graduation. 


#Returning home

Reasons for returning home
```{r}
#professional opportunites in HC
freq(Better.professional.opportunities.in.home.country)
```
This shows that better professional opportunities in respondents' home country was influential in their plan to return home after graduation.


```{r}
#quality of living in HC
freq(Better.quality.of.living.in.home.country)
```
This shows that better quality of living respondents' home country was influential in their plan to return home after graduation.


```{r}
#feeling comfortable at home
freq(Feeling.more.comfortable.at.home)
```
This shows that feeling more comfortable in respondents' home country was influential in their plan to return home after graduation.


```{r}
#income levels
freq(Higher.income.levels)
```
This shows that higher income levels in respondents' home country was influential in their plan to return home after graduation.

```{r}
#family ties in HC
freq(Family.ties.back.home)

```
This shows that family ties back home was influential in respondents' plan to return home after graduation.



Reasons for Leaving Russia to Return Home
```{r}
#feeling of alienation
freq(Feelings.of.alienation.from.the.Russian.culture.and.population)
```
This shows that feeling of alientation from the Russian culture and people was not influential in respondents' plan leave Russia after graduation.


```{r}
#finding jobs
freq(Difficulties.in.finding.a.job)
```
This shows that difficulty in finding a job in Russia was influential in respondents' plan to leave after graduation.

```{r}
#working conditions
freq(Poor.working.conditions)
```
This shows that respondents were uncertain about the influence of poor working conditions in Russia in their plan to leave after graduation.

```{r}
#quality of life
freq(Lower.quality.of.life)

```
This shows that respondents were uncertain about the influence of lower qualiy of life in Russia in their plan to leave after graduation.

```{r}
#discrimination
freq(Perceived.or.experienced.discrimination)

```
This shows that respondents reported that perceived or experienced discriminations was not influential in their decision to leave after graduation.


```{r}
#crime and safety level
freq(Crime.and.low.level.of.safety)
```
Respondents reported that crime and low level of safety in Russia was not influential in their decision to leave after graduation.


```{r}
#immigration process
freq(Strict.migration.process.difficulties.in.getting.visas.)

```
Respondents reported that Russia's stict migration process was influential in their decision to leave after graduation.


#Moving to another country

Reasons for moving to another country

```{r}
#job opportunities
freq(Better.job.opportunities)
```
Respondents reported that their plan to move to another country after graduation was influenced by better job opportunities in that country. 


```{r}
#quality of life
freq(Higher.quality.of.life)
```
Respondents reported that their plan to move to another country after graduation was influenced by higher quality of life in that country.

```{r}
#career opportunities
freq(Better.career.opportunities.and.advancement.in.chosen.profession.1)
```
Respondents reported that their plan to move to another country after graduation was influenced by better career opportunities in that country.

```{r}
#income levels
freq(Higher.income.levels.1)
```
Respondents reported that their plan to move to another country after graduation was influenced by higher income levels in that country.

```{r}
#ties to family and friends
freq(Ties.to.family.and.friends.1)
```
Respondents reported that their plan to move to another country after graduation was not influenced by better job opportunities in that country.

```{r}
#international experience
freq(Gain.international.experience.1)
```
Respondents reported that desire to gain international experience influenced their plan to move to another country after graduation.


```{r}
#immigration process
freq(Flexible.immigration.process)
```
Respondents reported that flexible immigration process influenced their plan to move to another country after graduation.


Reasons for Leaving Russia to move to another country
```{r}
#feeling of aliention 
freq(Feelings.of.alienation.from.the.Russian.culture.and.population.1)
```
This shows that feeling of alientation from the Russian culture and people was not influential in respondents' plan leave Russia after graduation.

```{r}
#finding jobs 
freq(Difficulties.in.finding.a.job.1)
```
This shows that difficulty in finding a job was influential in respondents' plan leave Russia after graduation.

```{r}
#working conditions 
freq(Poor.working.conditions.1)
```
This shows that poor working conditions was influential in respondents' plan leave Russia after graduation.

```{r}
#discrimination 
freq(Perceived.or.experienced.discrimination.1)
```
This shows that perceived or experienced discrimination was not influential in respondents' plan leave Russia after graduation.


```{r}
#crime and safetly level 
freq(Crime.and.low.level.of.safety.1)

```
This shows that crime and low level of saftey was not influential in respondents' plan leave Russia after graduation.

```{r}
#immigration process 
freq(Strict.migration.process.difficulties.in.getting.visas..1)

```
This shows that Russia' strict immigration process was not influential in respondents' plan leave Russia after graduation.


Reasons for not returning home but move to another country
```{r}
#family expectations 
freq(Family.expectations.1)
```
This shows that family expectations was not influential in respondents' plan to not return home after graduation.


```{r}
#cultural practices 
freq(Restrictive.cultural.practices..eg..pressure.to.marry..1)
```
This shows that restrictive cultural practices was not influential in respondents' plan to not return home after graduation.


```{r}
#limited job opportunities 
freq(Limited.job.opportunities.in.home.country.1)
```
This shows that limited job opportunities back home was influential in respondents' plan to not return home after graduation.

```{r}
#income levels
freq(Lower.income.levels.1)
```
This shows that lower income levels back home was influential in respondents' plan to not return home after graduation.

```{r}
#quality of life
freq(Lower.quality.of.life.3)

```
This shows that lower quality of life back home was influential in respondents' plan to not return home after graduation.

```{r}
#political persecution
freq(Political.persecution.1)
```
This shows that fear of political persecution back home was not influential in respondents' plan to not return home after graduation.


```{r}
#danger to one's life
freq(Danger.or.fear.for.one.s.own.life.1)

```
This shows that fear for one's own life back home was not influential in respondents' plan to not return home after graduation.






