---
title: "Data Analysis"
author: "Gabriel"
date: "March 22, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#defining the working directory
```{r}
getwd()
setwd("C:/Users/GHOOST/Desktop/New Lit/data")
```


#attaching the packages
```{r}
library(car)
library(foreign)
library(ggplot2)
library(gridExtra)
```

#attaching the data
```{r}
data<-read.csv("International Students Survey.csv")

attach(data)
```


#Data preparation

Age
```{r}
table(Age)

summary(as.numeric(Age))

data$age<-recode(as.numeric(Age),"17:21=1; 22:26=2;27:hi=3")

table(data$age)

data$age<-factor(data$age,lab=c("17 to 21 yrs", "22 to 26 yrs", " 27 yrs and older")) 

table(data$age)

```


country regions
```{r}
table(Home.country)

data$region[data$Home.country == 'Algeria'| 
    data$Home.country == 'Botswana'| data$Home.country == 'Cameroon'|
    data$Home.country == 'Chad'| data$Home.country == 'Congo'|
    data$Home.country == 'DR Congo'|data$Home.country == 'Eritrea'|
    data$Home.country == 'Ivory Coast'|
    data$Home.country == 'Gambia'|data$Home.country == 'Ghana'|
    data$Home.country == 'Kenya'|data$Home.country == 'Madagascar'|
    data$Home.country == 'Niger'|data$Home.country == 'Nigeria'|
    data$Home.country == 'South Africa'|data$Home.country == 'Sudan'|
    data$Home.country == 'Uganda'|data$Home.country == 'Zambia'] <- 'Africa'


data$region[data$Home.country == 'Australia'| data$Home.country == 'Austria'| 
    data$Home.country == 'Bosnia and Herzegovina'|
    data$Home.country == 'Bulgaria'| data$Home.country == 'Europe'|
    data$Home.country == 'France'| data$Home.country == 'Germany'|
    data$Home.country == 'Italy'|data$Home.country == 'Poland'|
    data$Home.country == 'Portugal'|data$Home.country == 'Serbia'|
    data$Home.country == 'Spain'|data$Home.country == 'Switzerland'|
    data$Home.country == 'Republic of North Macedonia'|
    data$Home.country == 'USA'] <- 'Europe, USA & Australia'


data$region[data$Home.country == 'Armenia'| 
    data$Home.country == 'Azerbaijan'|data$Home.country == 'Belarus'|
    data$Home.country == 'Estonia'|data$Home.country == 'Georgia'|
    data$Home.country == 'Georgia'|data$Home.country == 'Kazakhstan'|
    data$Home.country == 'Kyrgyzstan'|data$Home.country == 'Latvia'|
    data$Home.country == 'Moldova'|data$Home.country == 'Tajikistan'|
    data$Home.country == 'Turkmenistan'|data$Home.country == 'Ukraine'|
    data$Home.country == 'Uzbekistan'] <- 'Former Soviet Republics'


data$region[data$Home.country == 'Bahrain'| 
    data$Home.country == 'Egypt'| data$Home.country == 'Iran'|
    data$Home.country == 'Israel'| data$Home.country == 'Lebanon'|
    data$Home.country == 'Syria'| 
    data$Home.country == 'Turkey'] <- 'Middle East'


data$region[data$Home.country == 'Bangladesh'| 
    data$Home.country == 'India'| data$Home.country == 'Nepal'|
    data$Home.country == 'Pakistan'| 
    data$Home.country == 'Sri Lanka'] <- 'Southern Asia'

data$region[data$Home.country == 'Brazil'| 
    data$Home.country == 'Colombia'|data$Home.country == 'Ecuador'|
    data$Home.country == 'Guatemala'| data$Home.country == 'Haiti'|
    data$Home.country == 'Mexico'|
    data$Home.country == 'Nicaragua'] <- 'Southern America'

data$region[data$Home.country == 'China'| 
    data$Home.country == 'Japan'|data$Home.country == 'Mongolia'| 
    data$Home.country == 'South Korea'|data$Home.country == 'Hong Kong'|
    data$Home.country == 'Taiwan'] <- 'Eastern Asia'

data$region[data$Home.country == 'Indonesia'|
    data$Home.country == 'Philippines'|data$Home.country == 'Thailand'|
    data$Home.country == 'Vietnam'] <- 'Southern Eastern Asia'

table(data$region, useNA = "ifany")

attach(data)


```


##Descriptive Statistics

#background information
```{r}
#degree
table(What.degree.are.you.currently.studying.for.)
plot1 <-ggplot(data, aes(x=What.degree.are.you.currently.studying.for., fill=region)) + geom_bar() + labs(title="Degree")
print(plot1)

#language of instruction
table(What.is.the.language.of.instruction.for.your.program.)
plot2 <- ggplot(data, aes(x=What.is.the.language.of.instruction.for.your.program., fill=region)) + geom_bar() + labs(title="Language of instruction")
print(plot2)

#length of stay in Russia
table(How.long.have.you.been.in.Russia.studying.for.your.current.program.)
plot3 <- ggplot(data, aes(x=How.long.have.you.been.in.Russia.studying.for.your.current.program., fill=region)) + geom_bar() + labs(title="Length of stay in Russia")
print(plot3)

#financing status
table(How.are.you.financing.your.participation.in.the.program.)
plot4 <- ggplot(data, aes(x=How.are.you.financing.your.participation.in.the.program., fill=region)) + geom_bar() + labs(title="Financing Status")
print(plot4)

#ever been in Russia
table(Have.you.ever.been.in.Russia.before.you.enrolled.for.your.current.program)
plot5 <- ggplot(data, aes(x=Have.you.ever.been.in.Russia.before.you.enrolled.for.your.current.program, fill=region)) + geom_bar() + labs(title="Previous Stay in Russia")
print(plot5)

```

#Demographic 
```{r}
#Gender
table(Gender)
ggplot(data, aes(x=Gender, fill=region)) + geom_bar() + labs(title="Gender")

#Age
table(age)
ggplot(data, aes(x=age, fill=region)) + geom_bar() + labs(title="Age")

#family status
table(Family.status)
ggplot(data, aes(x=Family.status, fill=region)) + geom_bar() + labs(title="Family status")

#family income status
table(What.was.your.annual.family.income.when.you.were.applying.to.study.abroad..estimate.in.US.dollars.)
ggplot(data, aes(x=What.was.your.annual.family.income.when.you.were.applying.to.study.abroad..estimate.in.US.dollars., fill=region)) + geom_bar() + labs(title="Annual family income")

```


##Factors influencing the decision to study in Russia

#push factors in Home country
```{r}
#unvailable program
table(Unavailability.of.the.desired.study.program)
plot6 <-ggplot(data, aes(x=Unavailability.of.the.desired.study.program, fill=region)) + geom_bar() + labs(title="Unavailable program")
print(plot6)

#low quality of education
table(Low.quality.of.education)
plot7 <-ggplot(data, aes(x=Low.quality.of.education, fill=region)) + geom_bar() + labs(title="Low quality of education")
print(plot7)

#competive Uni admission
table(Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution)
plot8 <-ggplot(data, aes(x=Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution, fill=region)) + geom_bar() + labs(title="Competitive University Admission")
print(plot8)

#advantage of international degree
table(Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market)
plot9 <-ggplot(data, aes(x=Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market, fill=region)) + geom_bar() + labs(title="Perceived advantage of internatioal degree")
print(plot9)

#unavailability of scholarship
table(Unavailability.of.scholarship.opportunities)
plot10 <-ggplot(data, aes(x=Unavailability.of.scholarship.opportunities, fill=region)) + geom_bar() + labs(title="Unavailability of scholarship")
print(plot10)

#encouragement from family
table(Encouragement.from.my.family.to.study.abroad)
plot11 <-ggplot(data, aes(x=Encouragement.from.my.family.to.study.abroad, fill=region)) + geom_bar() + labs(title="Encouragement from family")
print(plot11)

#encouragement from friends
table(Encouragement.from..my.friends.to.study.abroad)
plot12 <-ggplot(data, aes(x=Encouragement.from..my.friends.to.study.abroad, fill=region)) + geom_bar() + labs(title="Encouragement from friends")
print(plot12)

#earning prospects
table(Better.earning.prospects.abroad)
plot13 <-ggplot(data, aes(x=Better.earning.prospects.abroad, fill=region)) + geom_bar() + labs(title="Better earning prospects")
print(plot13)

#social prestige
table(The.social.prestige.of.studying.abroad)
plot14 <-ggplot(data, aes(x=The.social.prestige.of.studying.abroad , fill=region)) + geom_bar() + labs(title="The.social.prestige.of.studying.abroad")
print(plot14)

#experience different culture
table(To.experience.a.different.culture)
plot15 <-ggplot(data, aes(x=To.experience.a.different.culture, fill=region)) + geom_bar() + labs(title="EXperience different culture")
print(plot15)

```

#pull factors in Russia
```{r}
#available program
table(Availability.of.desired.study.program)
plot16 <-ggplot(data, aes(x=Availability.of.desired.study.program, fill=region)) + geom_bar() + labs(title="Availability of desired study program")
print(plot16)

#high quality of education
table(Higher.quality.of.education..compared.to.home.country.)
plot17 <-ggplot(data, aes(x=Higher.quality.of.education..compared.to.home.country., fill=region)) + geom_bar() + labs(title="High quality of education")
print(plot17)

#low cost of living
table(Low.cost.of.living)
plot18 <-ggplot(data, aes(x=Low.cost.of.living, fill=region)) + geom_bar() + labs(title="Low cost of living")
print(plot18)

#low tuition fees
table(Low.tuition.fees)
plot19 <-ggplot(data, aes(x=Low.tuition.fees, fill=region)) + geom_bar() + labs(title="Low tuition fees")
print(plot19)

#scholarships
table(Awarded.scholarships.or.tuition.waiver)
plot20 <-ggplot(data, aes(x=Awarded.scholarships.or.tuition.waiver, fill=region)) + geom_bar() + labs(title="Scholarship or tuition waiver")
print(plot20)

#attraction to Russian culture
table(Attraction.to.Russian.culture..society)
plot21 <-ggplot(data, aes(x=Attraction.to.Russian.culture..society, fill=region)) + geom_bar() + labs(title="Attraction to Russian culture")
print(plot21)

#career prospects in Russia
table(Career.prospects.in.Russia)
plot22 <-ggplot(data, aes(x=Career.prospects.in.Russia, fill=region)) + geom_bar() + labs(title="Career prospects in Russia")
print(plot22)

#recommendations from family and friends
table(Personal.recommendations.from.parents..relatives..and.friends)
plot23 <-ggplot(data, aes(x=Personal.recommendations.from.parents..relatives..and.friends, fill=region)) + geom_bar() + labs(title="Recommendations from family and friends")
print(plot23)

#cultural proximity
table(cultural.proximity.with.home)
plot24 <-ggplot(data, aes(x=cultural.proximity.with.home, fill=region)) + geom_bar() + labs(title="Cultural proximity")
print(plot24)

#geographical proximity
table(geographical.proximity.with.home)
plot25 <-ggplot(data, aes(x=geographical.proximity.with.home, fill=region)) + geom_bar() + labs(title="Geograhical proximity")
print(plot25)


```

#Pull Factors in HSE
```{r}
#quality and reputation
table(Quality.and.reputation.of.the.University)
plot26 <-ggplot(data, aes(x=Quality.and.reputation.of.the.University, fill=region)) + geom_bar() + labs(title="Quality and reputation of HSE")
print(plot26)

#recognition of degree
table(Recognition.of.the.degree.in.my.home.country)
plot27 <-ggplot(data, aes(x=Recognition.of.the.degree.in.my.home.country, fill=region)) + geom_bar() + labs(title="Recognition of degree")
print(plot27)

#quality of teachers
table(Quality.of.the.teaching.staff)
plot28 <-ggplot(data, aes(x=Quality.of.the.teaching.staff, fill=region)) + geom_bar() + labs(title="Quality of teachers")
print(plot28)

#reputation of alumni
table(The.reputation.of.the.alumni)
plot29 <-ggplot(data, aes(x=The.reputation.of.the.alumni, fill=region)) + geom_bar() + labs(title="Reputation of alumni")
print(plot29)

#reputation of international community
table(The.reputation.of.the.international.community)
plot30 <-ggplot(data, aes(x=The.reputation.of.the.international.community, fill=region)) + geom_bar() + labs(title="Reputation of the international community")
print(plot30)

#HSE rank
table(HSE.position.in.international.university.rankings)
plot31 <-ggplot(data, aes(x=HSE.position.in.international.university.rankings, fill=region)) + geom_bar() + labs(title="HSE's rank")
print(plot31)

#cost of tuition
table(Cost.of.tuition.for.international.students)
plot32 <-ggplot(data, aes(x=Cost.of.tuition.for.international.students, fill=region)) + geom_bar() + labs(title="Cost of tuition")
print(plot32)

#availability of scholarships
table(Availability.of.scholarships)
plot33 <-ggplot(data, aes(x=Availability.of.scholarships, fill=region)) + geom_bar() + labs(title="Availability of scholarships")
print(plot33)

#support for international students
table(Support.services.for.international.students)
plot34 <-ggplot(data, aes(x=Support.services.for.international.students, fill=region)) + geom_bar() + labs(title="Support services for international students")
print(plot34)

#graduate employment
table(Graduates.employment.rates)
plot35 <-ggplot(data, aes(x=Graduates.employment.rates, fill=region)) + geom_bar() + labs(title="Graduate employment")
print(plot35)

#HSE alliances
table(HSE.s.international.strategic.alliances)
plot36 <-ggplot(data, aes(x=HSE.s.international.strategic.alliances, fill=region)) + geom_bar() + labs(title="HSE alliances")
print(plot36)

#local preference for HSE degree
table(Local.employers.preference.of..degrees.awarded.by.HSE)
plot37 <-ggplot(data, aes(x=Local.employers.preference.of..degrees.awarded.by.HSE, fill=region)) + geom_bar() + labs(title="Local preference for HSE degrees")
print(plot37)

```


##Regression for factors influencing the decision to move to Russia

#Push Factors

empty model
```{r}
model0<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~1, data = data)
summary(model0)

```


Model 1 (for the entire data)
```{r}
model1<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture, data = data)

summary(model1)
```


Model 2 (for Africa)
```{r}
model2<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Africa"))

summary(model2)

```


Model 3 (for Eastern ASia)
```{r}
model3<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Eastern Asia"))

summary(model3)
```


Model 4 (for Europe, USA & Australia)
```{r}
model4<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Europe, USA & Australia"))

summary(model4)

```


Model 5 (Former Soviet Republics)
```{r}
model5<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Former Soviet Republics"))

summary(model5)
```


Model 6 (Middle East)
```{r}
model6<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Middle East"))

summary(model6)
```


Model 7 (Southern America)
```{r}
model7<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture, data = subset(data, region=="Southern America"))

summary(model7)


```


Model 8 (Southern Asia)
```{r}
model8<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Southern Asia"))

summary(model8)

table(region)
```


Model 9 (Southern Eastern Asia)
```{r}
model9<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Southern Eastern Asia"))

summary(model9)

```


#Pull Factors

Pull Factors in Russia
```{r}

model10<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home, data=data)

summary(model10)
```


Pull Factors in HSE
```{r}

model11<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE, data = data)

summary(model11)
```

Pull factors (Both Russia and HSE)
```{r}
model12<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home+Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE, data=data)

summary(model12)
```


Model 13 (for Africa)
```{r}
model13<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home+Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE+as.numeric(age)+Gender, data = subset(data, region=="Africa"))

summary(model13)

```


Model 14 (for Eastern ASia)
```{r}
model14<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home+Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE+as.numeric(age)+Gender, data = subset(data, region=="Eastern Asia"))

summary(model14)
```


Model 15 (for Europe, USA & Australia)
```{r}
model15<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home+Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE+as.numeric(age)+Gender, data = subset(data, region=="Europe, USA & Australia"))

summary(model15)

```


Model 16 (Former Soviet Republics)
```{r}
model16<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home+Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE, data = subset(data, region=="Former Soviet Republics"))

summary(model16)

```


Model 17 (Middle East)
```{r}
model17<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home+Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE, data = subset(data, region=="Middle East"))

summary(model17)
```


Model 18 (Southern America)
```{r}
model18<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home+Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE, data = subset(data, region=="Southern America"))

summary(model18)


```


Model 19 (Southern Asia)
```{r}
model19<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Southern Asia"))

summary(model19)

table(region)
```


Model 20 (Southern Eastern Asia)
```{r}
model9<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Southern Eastern Asia"))

summary(model20)

```


































##Post graduation migration plans

#graduation plans
```{r}
table(What.are.your.plans.after.graduation.)

```

#staying in Russia
```{r}

table(What.will.be.your.reason.for.staying.in.Russia.after.graduation.)
```

Reason for staying in Russia
```{r}
#job opportunities
table(Better.job.opportunities..in.comparison.with.home.country.)

#quality of life
table(Higher.quality.of.life..in.comparison.with.home.country.)

#career opportunities
table(Better.career.opportunities.and.advancement.in.chosen.profession)

#income level
table(Higher.income.level)

#ties to family and friends
table(Ties.to.family.and.friends)

#international experience
table(Gain.international.experience)

#Indicate.any.other.factor.that.has.influenced.your.plan.to.stay.in.Russia.after.graduation
```

Reasons for not returning home but stay in Russia
```{r}
#family expectations
table(Family.expectations)

#cultural practices
table(Restrictive.cultural.practices..eg..pressure.to.marry.)

#limited job opportunitiesin Home country
table(Limited.job.opportunities.in.home.country)

#income levels
table(Lower.income.levels)

#quality of life
table(Lower.quality.of.life.2)

#political persecution
table(Political.persecution)

#danger to one's life
table(Danger.or.fear.for.one.s.own.life)

#Indicate.any.other.factor.that.influenced.your.plan.not.to.return.home.after.graduation

```


#returning home
```{r}

table(What.will.be.your.reason.for.returning.home.after.graduation.)
```

Reasons for Leaving Russia to Return Home
```{r}
#feeling of alienation
table(Feelings.of.alienation.from.the.Russian.culture.and.population)

#finding jobs
table(Difficulties.in.finding.a.job)

#working conditions
table(Poor.working.conditions)

#quality of life
table(Lower.quality.of.life)

#discrimination
table(Perceived.or.experienced.discrimination)

#crime and safety level
table(Crime.and.low.level.of.safety)

#immigration process
table(Strict.migration.process.difficulties.in.getting.visas.)

#Indicate.any.other.factor.that.has.influenced.your.plan.to.leave.Russia.after.graduation
```

Reasons for returning home
```{r}
#professional opportunites in HC
table(Better.professional.opportunities.in.home.country)

#quality of living in HC
table(Better.quality.of.living.in.home.country)

#feeling comfortable at home
table(Feeling.more.comfortable.at.home)

#income levels
table(Higher.income.levels)

#family ties in HC
table(Family.ties.back.home)

#Indicate.any.other.factor.that.has.influenced.your.plan.to.return.home.after.graduation

```


#moving to another country
```{r}
table(What.will.be.your.reason.for.moving.to.another.country.after.graduation.)

#another country
#table(What.country..or.countries..are.you.considering.migrating.to.)
```


Reasons for Leaving Russia to move to another country
```{r}
#feeling of aliention 
table(Feelings.of.alienation.from.the.Russian.culture.and.population.1)

#finding jobs 
table(Difficulties.in.finding.a.job.1)

#working conditions 
table(Poor.working.conditions.1)

#discrimination 
table(Perceived.or.experienced.discrimination.1)

#crime and safetly level 
table(Crime.and.low.level.of.safety.1)

#immigration process 
table(Strict.migration.process.difficulties.in.getting.visas..1)

#Indicate.any.other.factor.that.has.influenced.your.plan.to.leave.Russia.after.graduation.1

```


Reasons for not returning home but move to another country
```{r}
#family expectations 
table(Family.expectations.1)

#cultural practices 
table(Restrictive.cultural.practices..eg..pressure.to.marry..1)

#limited job opportunities 
table(Limited.job.opportunities.in.home.country.1)

#income levels
table(Lower.income.levels.1)

#quality of life
table(Lower.quality.of.life.3)

#political persecution
table(Political.persecution.1)

#danger to one's life
table(Danger.or.fear.for.one.s.own.life.1)

#Indicate.any.other.factor.that.influenced.your.plan.not.to.return.home.after.graduation.1
```

Reasons for moving to another country
```{r}
#job opportunities
table(Better.job.opportunities)

#quality of life
table(Higher.quality.of.life)

#career opportunities
table(Better.career.opportunities.and.advancement.in.chosen.profession.1)

#income levels
table(Higher.income.levels.1)

#ties to family and friends
table(Ties.to.family.and.friends.1)

#international experience
table(Gain.international.experience.1)

#immigration process
table(Flexible.immigration.process)

#Indicate.any.other.factor.that.has.influenced.your.plan.to.move.to.another.country.after.graduation
```



#Regression for factors influencing the decision to move to Russia

Push Factors
```{r}

model1<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture, data = data)

summary(model1)
```

Pull Factors in Russia
```{r}

model2<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Availability.of.desired.study.program+Higher.quality.of.education..compared.to.home.country.+Low.cost.of.living+Low.tuition.fees+Awarded.scholarships.or.tuition.waiver+Attraction.to.Russian.culture..society+Career.prospects.in.Russia+Personal.recommendations.from.parents..relatives..and.friends+cultural.proximity.with.home+geographical.proximity.with.home, data=data)

summary(model2)
```


Pull Factors in HSE
```{r}

model3<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Quality.and.reputation.of.the.University+Recognition.of.the.degree.in.my.home.country+Quality.of.the.teaching.staff+The.reputation.of.the.alumni+The.reputation.of.the.international.community+HSE.position.in.international.university.rankings+Cost.of.tuition.for.international.students+Availability.of.scholarships+Support.services.for.international.students+Graduates.employment.rates+HSE.s.international.strategic.alliances+Local.employers.preference.of..degrees.awarded.by.HSE, data = data)

summary(model3)
```

Multilevel 
```{r}
library(psych)
library(lmtest)
library(car)
library(foreign)
library(lme4)
library(sjPlot)
library(ggplot2)
library(ggrepel)
library(influence.ME)
library(mitml)
library(ICC)

  
```



```{r}
model4a<-lmerTest::lmer(as.numeric(What.degree.are.you.currently.studying.for.)~(1 | Home.country), REML = FALSE, data = data)

summary(model4a)
summary(model4a)

ICCbare(Home.country, as.numeric(What.degree.are.you.currently.studying.for.), data)


plot_model(model4a, type = "re", sort.est = "sort.all", grid = F)
```


```{r}
model5a <- lmerTest::lmer(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+(1 | Home.country), REML = FALSE, data = data)

summary(model5a)
```



```{r}

model7<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture+as.numeric(age)+Gender, data = subset(data, region=="Africa"))

summary(model7)
```



```{r}
model8<-lm(as.numeric(What.degree.are.you.currently.studying.for.)~Unavailability.of.the.desired.study.program+Low.quality.of.education+ Competitive.university.admission.process..difficult.to.gain.admission.to.a.quality.local.institution+ Perceived.advantage.of.international.degree.over.a.local.one.at.the.local.job.market+ Unavailability.of.scholarship.opportunities+ Encouragement.from.my.family.to.study.abroad+ Encouragement.from..my.friends.to.study.abroad+ Better.earning.prospects.abroad+ The.social.prestige.of.studying.abroad+ To.experience.a.different.culture, data = subset(data, region=="Former Soviet Republics"))

summary(model8)
```




